Quantifying the global film festival circuit: networks, diversity and value creation

### 2023-03-10 cudan/paperplots.qmd
news
edges

```{r}
library(plotly)
library(tidyverse)
library(colorspace)
library(ggbeeswarm)
library(ggrepel)
library(patchwork)
library(visNetwork)
library(rworldmap)
library(scales)
# library(lemon)

@@

```{r}
attr(nodelist, "info") %>% cat
```

>>>>

```{r}
library(plotly)
library(tidyverse)
library(colorspace)
library(ggbeeswarm)
library(ggrepel)
library(patchwork)
library(visNetwork)
library(rworldmap)
library(scales)
library(igraph)
# library(lemon)

@@

```{r}
attr(nodelist, "info") %>% cat

```{r}
graph_from_data_frame(e2, directed = F, vertices = nodelist) %>% ecount() %>% paste( "edges") %>% cat
```
